---
title: "Homework 6"
author: "Philip Kim"
date: "11/29/2021"
output: 
  github_document:
    toc: true
    toc_depth: 6
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(purrr)
library(knitr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


# Problem 1

## Load and tidy data

```{r, message = FALSE}
birthweight_df =
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace))

sum(is.na(birthweight_df))
```

## Regression Model

In efforts to propose a regression model for birthweight, I hypothesized that the biological features of the mother, during the time of delivery, were the most important factors. As such, the variables of interest were `delwt`, `mheight`, `momage`, and `mrace`. 

```{r, message = FALSE}
model = lm(bwt ~ delwt + mheight + momage + mrace, data = birthweight_df)

model %>% broom::tidy()

birthweight_df %>% 
  add_predictions(model) %>% 
  add_residuals(model) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(
    x = "Fitted Values",
    y = "Residuals",
    title = "Model Residuals against Fitted Values" ) +
   theme(plot.title = element_text(hjust = 0.5))
```

## Model comparison

```{r}
model2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)

model3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight_df)
```

### Cross-Validation

```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    model = map(train, ~lm(bwt ~ delwt + mheight + momage + mrace, data = .x)),
    model2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model3 = map(train, ~lm(bwt ~ bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))) %>% 
  mutate(
    rmse_model = map2_dbl(model, test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
    rmse_model3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot() +
  labs(
    x = "Model",
    y = "RMSE",
    title = "RMSE for 3 Models") +
  theme(plot.title = element_text(hjust = 0.5))
```


# Problem 2

```{r, message = FALSE}
set.seed(1)

weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## R_hat_squared

```{r}
r_hat_squared = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)
```

### Confidence Interval

```{r}
r_hat_squared %>% 
  summarize(
    lower = quantile(r.squared, 0.025),
    upper = quantile(r.squared, 0.975)) %>% 
  kable()
```

### Distribution Plot

```{r}
r_hat_squared %>% 
  ggplot(aes(x = r.squared)) + 
  geom_density() +
  labs(
    x = "R hat squared",
    y = "Density",
    title = "Distribution of R hat squared estimated values") +
  theme(plot.title = element_text(hjust = 0.5))
```

## Log(b0 * b1)

```{r}
log_b0_b1 = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results) %>% 
  select(strap_number:estimate) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate") %>% 
  janitor::clean_names() %>% 
  mutate(
    new_log = log(intercept * tmin)
    )
```

### Confidence Interval

```{r}
log_b0_b1 %>% 
  summarize(
    lower = quantile(new_log, 0.025),
    upper = quantile(new_log, 0.975)) %>% 
  kable()
```

### Distribution Plot

```{r}
log_b0_b1 %>% 
  ggplot(aes(x = new_log)) + 
  geom_density() +
  labs(
    x = "log(b0 * b1)",
    y = "Density",
    title = "Distribution of log(b0 *b1) estimated values") +
  theme(plot.title = element_text(hjust = 0.5))
```

